25 years of Social Work Research

### 2015-03-31 dataCleaning.Rmd
Minor edit - reads in rankSet.csv

```{r initialization}
rm(list=ls())  
load("/Users/beperron/Git/SocialWorkResearch/socialWorkHistory.Rdata")
#load("/Users/SSW/Documents/GitHub/SocialWork100Years/socialWorkHistory.Rdata")

@@

```{r eval=FALSE}
# Read data files
#load("/Users/beperron/Git/SocialWorkResearch/Data/ebscoFULL.R")
#load("/Users/beperron/Git/SocialWorkResearch/Data/proQuest.R")
#hodge <- readLines("/Users/beperron/Git/SocialWorkResearch/search_specifications/hodge.txt", n = -1)
#countries.csv <- read.csv("/Users/beperron/Git/SocialWorkResearch/Data/countries.csv")
load("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/ebscoFULL.R")
load("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/proQuest.R")
hodge <- readLines("/Users/SSW/Documents/GitHub/SocialWork100Years/search_specifications/hodge.txt", n = -1)
countries.csv<-read.csv("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/countries.csv")

# Load special functions
source("/Users/beperron/Git/SocialWorkResearch/functions/appendData.R")
source("/Users/beperron/Git/SocialWorkResearch/functions/shortArticles.R")
source("/Users/beperron/Git/SocialWorkResearch/functions/titleMatching.R")
source("/Users/beperron/Git/SocialWorkResearch/functions/otherDocuments.R")
source("/Users/beperron/Git/SocialWorkResearch/functions/titleMatching.R")
source("/Users/beperron/Git/SocialWorkResearch/functions/fewArticles.R")

#source("/Users/SSW/Documents/GitHub/SocialWork100Years/functions/appendData.R")
#source("/Users/SSW/Documents/GitHub/SocialWork100Years/functions/shortArticles.R")
#source("/Users/SSW/Documents/GitHub/SocialWork100Years/functions/titleMatching.R")
#source("/Users/SSW/Documents/GitHub/SocialWork100Years/functions/otherDocuments.R")
#source("/Users/SSW/Documents/GitHub/SocialWork100Years/functions/titleMatching.R")
#source("/Users/SSW/Documents/GitHub/SocialWork100Years/functions/fewArticles.R")

@@

```{r appendData, comment=NA, echo=FALSE, eval=FALSE}
appendData.f()

@@

```{r shortArticles, comment=NA, echo=FALSE, warning=FALSE, eval=FALSE}
shortArticles.f()
```

```{r titleMatching, echo=FALSE, eval=FALSE}
titleMatching.f()

@@

```{r otherDocuments, echo=FALSE, eval=FALSE}
otherDocuments.f()
articles.otherDocuments <- length(which(full.df$attributes == "article"))
journals.otherDocuments <- filter(full.df, attributes == "journal") %>% 
    summarise(Unique = n_distinct(record))
```

```{r final, comment=NA, echo=FALSE, eval=FALSE}
fewArticles.f()
articles.final <- length(which(full.df$attributes == "article"))
journals.final <- filter(full.df, attributes == "journal") %>% 
    summarise(Unique = n_distinct(record))
```

```{r finalList, comment=NA, echo=FALSE, eval=FALSE}
unique.titles <- filter(full.df, attributes == "journal") %>%
    group_by(record) %>%
    summarise(N = n())

@@

```{r plotArticleCount, eval=FALSE}
n.articles.year <- filter(full.df, attributes == "pubYear") 
year.split <- split(n.articles.year, n.articles.year$record)
year.count <- unlist(lapply(year.split, nrow))
year.count <- year.count[order(names(year.count))]
years <- names(year.count)

@@

```{r plotJournalCount, eval=FALSE}
n.journals.year <- filter(full.df, attributes == "journal") %>%
    select(articleID, record)

@@

```{r plotAuthorCount, eval=FALSE}

@@

```{r locationExtraction2, eval=FALSE}
LO.df2 <- filter(full.df, attributes == "abstract" |
                 attributes == "article" | attributes == "keyword")
indx.country <- paste(countries.csv$x, collapse = "[\\s|[[:punct:]]]|")
library(stringi)
countries.extracted <- na.omit(within(LO.df2, text1<- stri_extract(LO.df2$record, opts_fixed=TRUE, regex=indx.country)))[-2]
countries.extracted$text1<-gsub("[[:punct:]]", "", countries.extracted$text1)
countries.extracted$text1<-gsub("^\\s+|\\s+$", "", countries.extracted$text1)

@@

setwd("C:/Users/SSW/Documents/GitHub/SocialWork100Years/Data")
GDP<-read.csv("GDP.csv")
GDP<-select(GDP, Country=Country.Name, GDPperCapita=GDPperCapita2013, GDPRank)

PPP<-read.csv("PPP.csv")
PPP$PPP2013<-gsub(",", "", PPP$PPP2013)
PPP$PPP2013<-as.character(PPP$PPP2013)
PPP$PPP2013<-as.numeric(PPP$PPP2013)

articleCountries<-table(locations$record)
articleCountries<-as.data.frame(articleCountries)
articleCountries<-articleCountries%>%
                    select(Country=Var1, articleCount=Freq)

rankSet<-merge(articleCountries, GDP, by="Country", all=TRUE)
rankSet$articleCount[is.na(rankSet$articleCount)]<-0
rankSet<-merge(rankSet, PPP, by="Country", all=TRUE)

rankSet<-mutate(rankSet, articleRank=rank(-articleCount))
```

```{r worldmap, eval=FALSE}

@@

```{r locationWithtUS, eval=FALSE}
year.df <- filter(full.df, attributes == "pubYear") %>%
            select(articleID, record)

@@

```{r plotLocationWithUS, eval=FALSE}

@@

```{r nsf, eval=FALSE}
nsf <- data.frame(c(rep(NA, 13), 238, 273, 304, 323, 308, 287, 338, 332, 308, 289, 280, NA), as.factor(seq(1989,2013, 1)))

@@

```{r nsfPlot, eval=FALSE}
plot.PhD <- ggplot(nsf, aes(years, n.grads, group=1)) + 
    geom_line(linetype="dotted", colour = "#0072B2", size = .75) + 
    geom_point(colour = "#0072B2", size = .75) +
     scale_y_continuous(breaks = c(seq(0, 350, 25)), limits = c(200,350)) +
     ylab("Doctoral degrees") +
     xlab("Year") +
     geom_text(aes(label = n.grads), vjust = -1.2, size = 2.75) + 
     theme(axis.text.x = element_text(angle = 45, hjust = 1), 
           title = element_text(size = 10)) +
     ggtitle("Number of Earned Social Work Doctoral Degrees by Year") 
```

```{r pages, eval=FALSE}
pages.df <- full.df %>% filter(attributes == "pages")
page.identifier <- grepl("[-p]", pages.df$record)
pages.df.reduced <- pages.df[page.identifier == FALSE,]

@@

```{r eval=FALSE}
save.image(file = "socialWorkHistory.Rdata")
```

@@

```{r message=FALSE, warning=FALSE, eval=FALSE}
cor.data <- select(final.list, first, last, n) %>%
            mutate(no.years = as.numeric(last) - as.numeric(first))

@@

```{r eval=FALSE}
journalArticleFinder.f <- function(journalTitle, keyword = FALSE, 
                           authorAff = FALSE, abstract = FALSE){
    article.search <- which(full.df$record == journalTitle)
    article.search <- full.df[article.search,]
    article.search.ID <- select(article.search, articleID)
    target.ID <- full.df$articleID %in% article.search.ID$articleID
    journal.article.df <- full.df[target.ID, ]
    journal.article.df <- filter(journal.article.df, attributes == "article")
    journal.article.df <- arrange(journal.article.df, record)
    if(keyword == FALSE){journal.article.df <- filter(journal.article.df, attributes != "keyWord")}
    if(authorAff == FALSE){journal.article.df <- filter(journal.article.df, attributes != "authorAff")}
    if(abstract == FALSE){journal.article.df <- filter(journal.article.df, attributes != "abstract")}
    x.shortened <- gsub(" ", "", journalTitle)
    write.csv(journal.article.df, file = paste0(x.shortened, ".csv"), row.names=F)
    }

>>>>

```{r initialization}
rm(list=ls())  
#load("/Users/beperron/Git/SocialWorkResearch/socialWorkHistory.Rdata")
#load("/Users/SSW/Documents/GitHub/SocialWork100Years/socialWorkHistory.Rdata")

@@

```{r eval=TRUE}
# Read data files
#load("/Users/beperron/Git/SocialWorkResearch/Data/ebscoFULL.R")
#load("/Users/beperron/Git/SocialWorkResearch/Data/proQuest.R")
#hodge <- readLines("/Users/beperron/Git/SocialWorkResearch/search_specifications/hodge.txt", n = -1)
#countries.csv <- read.csv("/Users/beperron/Git/SocialWorkResearch/Data/countries.csv")
load("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/ebscoFULL.R")
load("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/proQuest.R")
hodge <- readLines("/Users/SSW/Documents/GitHub/SocialWork100Years/search_specifications/hodge.txt", n = -1)
countries.csv<-read.csv("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/countries.csv")

# Load special functions
#source("/Users/beperron/Git/SocialWorkResearch/functions/appendData.R")
#source("/Users/beperron/Git/SocialWorkResearch/functions/shortArticles.R")
#source("/Users/beperron/Git/SocialWorkResearch/functions/titleMatching.R")
#source("/Users/beperron/Git/SocialWorkResearch/functions/otherDocuments.R")
#source("/Users/beperron/Git/SocialWorkResearch/functions/titleMatching.R")
#source("/Users/beperron/Git/SocialWorkResearch/functions/fewArticles.R")

source("/Users/SSW/Documents/GitHub/SocialWork100Years/functions/appendData.R")
source("/Users/SSW/Documents/GitHub/SocialWork100Years/functions/shortArticles.R")
source("/Users/SSW/Documents/GitHub/SocialWork100Years/functions/titleMatching.R")
source("/Users/SSW/Documents/GitHub/SocialWork100Years/functions/otherDocuments.R")
source("/Users/SSW/Documents/GitHub/SocialWork100Years/functions/titleMatching.R")
source("/Users/SSW/Documents/GitHub/SocialWork100Years/functions/fewArticles.R")

@@

```{r appendData, comment=NA, echo=FALSE, eval=TRUE}
appendData.f()

@@

```{r shortArticles, comment=NA, echo=FALSE, warning=FALSE, eval=TRUE}
shortArticles.f()
```

```{r titleMatching, echo=FALSE, eval=TRUE}
titleMatching.f()

@@

```{r otherDocuments, echo=FALSE, eval=TRUE}
otherDocuments.f()
articles.otherDocuments <- length(which(full.df$attributes == "article"))
journals.otherDocuments <- filter(full.df, attributes == "journal") %>% 
    summarise(Unique = n_distinct(record))
```

```{r final, comment=NA, echo=FALSE, eval=TRUE}
fewArticles.f()
articles.final <- length(which(full.df$attributes == "article"))
journals.final <- filter(full.df, attributes == "journal") %>% 
    summarise(Unique = n_distinct(record))
```

```{r finalList, comment=NA, echo=FALSE, eval=TRUE}
unique.titles <- filter(full.df, attributes == "journal") %>%
    group_by(record) %>%
    summarise(N = n())

@@

```{r plotArticleCount, eval=TRUE}
n.articles.year <- filter(full.df, attributes == "pubYear") 
year.split <- split(n.articles.year, n.articles.year$record)
year.count <- unlist(lapply(year.split, nrow))
year.count <- year.count[order(names(year.count))]
years <- names(year.count)

@@

```{r plotJournalCount, eval=TRUE}
n.journals.year <- filter(full.df, attributes == "journal") %>%
    select(articleID, record)

@@

```{r plotAuthorCount, eval=TRUE}

@@

```{r locationExtraction2, eval=TRUE}
LO.df2 <- filter(full.df, attributes == "abstract" |
                 attributes == "article" | attributes == "keyword")
indx.country <- paste(countries.csv$x, collapse = "[\\s|[[:punct:]]]|")
library(stringi)
countries.extracted <- na.omit(within(LO.df2, text1<- stri_extract(LO.df2$record, opts_fixed=TRUE, regex=indx.country)))[-2]
countries.extracted$text1<-gsub("[[:punct:]]", "", countries.extracted$text1)
countries.extracted$text1<-gsub("^\\s+|\\s+$", "", countries.extracted$text1)

@@

setwd("C:/Users/SSW/Documents/GitHub/SocialWork100Years/Data")
rankSet<-read.csv("rankSet.csv")

```{r worldmap, eval=TRUE}

@@

```{r locationWithtUS, eval=TRUE}
year.df <- filter(full.df, attributes == "pubYear") %>%
            select(articleID, record)

@@

```{r plotLocationWithUS, eval=TRUE}

@@

```{r nsf, eval=TRUE}
nsf <- data.frame(c(rep(NA, 13), 238, 273, 304, 323, 308, 287, 338, 332, 308, 289, 280, NA), as.factor(seq(1989,2013, 1)))

@@

```{r nsfPlot, eval=TRUE}
plot.PhD <- ggplot(nsf, aes(years, n.grads, group=1)) + 
    geom_line(linetype="dotted", colour = "#0072B2", size = .75) + 
    geom_point(colour = "#0072B2", size = .75) +
     scale_y_continuous(breaks = c(seq(0, 350, 25)), limits = c(200,350)) +
     ylab("Doctoral degrees") +
     xlab("Year") +
     geom_text(aes(label = n.grads), vjust = -1.2, size = 2.75) + 
     theme(axis.text.x = element_text(angle = 45, hjust = 1), 
           title = element_text(size = 10)) +
     ggtitle("Number of Earned Social Work Doctoral Degrees by Year") 
```

```{r pages, eval=TRUE}
pages.df <- full.df %>% filter(attributes == "pages")
page.identifier <- grepl("[-p]", pages.df$record)
pages.df.reduced <- pages.df[page.identifier == FALSE,]

@@

```{r eval=TRUE}
save.image(file = "socialWorkHistory.Rdata")
```

@@

```{r message=FALSE, warning=FALSE, eval=TRUE}
cor.data <- select(final.list, first, last, n) %>%
            mutate(no.years = as.numeric(last) - as.numeric(first))

@@

```{r eval=TRUE}
journalArticleFinder.f <- function(journalTitle, keyword = FALSE, 
                           authorAff = FALSE, abstract = FALSE){
    article.search <- which(full.df$record == journalTitle)
    article.search <- full.df[article.search,]
    article.search.ID <- select(article.search, articleID)
    target.ID <- full.df$articleID %in% article.search.ID$articleID
    journal.article.df <- full.df[target.ID, ]
    journal.article.df <- filter(journal.article.df, attributes == "article")
    journal.article.df <- arrange(journal.article.df, record)
    if(keyword == FALSE){journal.article.df <- filter(journal.article.df, attributes != "keyWord")}
    if(authorAff == FALSE){journal.article.df <- filter(journal.article.df, attributes != "authorAff")}
    if(abstract == FALSE){journal.article.df <- filter(journal.article.df, attributes != "abstract")}
    x.shortened <- gsub(" ", "", journalTitle)
    write.csv(journal.article.df, file = paste0(x.shortened, ".csv"), row.names=F)
    }
